\addcontentsline{toc}{chapter}{СПИСОК ИСПОЛЬЗОВАННЫХ ИСТОЧНИКОВ}

\begin{thebibliography}{3}
	
	\bibitem{zelenkov2007}
	
	Зеленков~Ю.Г., Сегалович~И.В. Сравнительное исследование методов определения нечетких дубликатов для Web-документов~// Труды 9-й Всероссийской научной конференции RCDL2007. --- Переславль-Залесский, 2007.
	
	\bibitem{cyberleninka_zaimstvovaniya}
	
	Гришин~В.Д. Методы анализа и поиска заимствований в тексте~// Актуальные проблемы гуманитарных и естественных наук. --- 2018. --- №~6.
	
	\bibitem{cyberleninka_dissertacii}
	
	Авдеева~Н.В., Ледовская~В.М. Некорректные заимствования в диссертациях: способы их обнаружения~// Высшее образование в России. --- 2015. --- №~6. --- С.~22--29.
	
	\bibitem{matec_winnowing2018}
	
	Implementation of Winnowing Algorithm Based K-Gram to Identify Plagiarism~// MATEC Web of Conferences. --- 2018. --- Vol.~154.
	
	\bibitem{mdpi_fingerprint2021}
	
	A Robust Document Identification Framework through f-BP Fingerprint~// Applied Sciences. --- 2021. --- Vol.~7, No.~8.
	
	\bibitem{tfidf_hybrid2022}
	
	Research on Text Similarity Measurement Hybrid Algorithm with TF-IDF Method~// Applied Mathematics. --- 2022.
	
	\bibitem{mit_levenshtein2020}
	
	Levenshtein Distance, Sequence Comparison and Biological Applications~// MIT Open Courseware. --- 2020.
	
	\bibitem{arxiv_bertembed2020}
	
	On the Sentence Embeddings from BERT for Semantic Textual Similarity~// Proceedings of EMNLP. --- 2020.
	
	\bibitem{aclan_phrase_bert2021}
	
	Phrase-BERT: Improved Phrase Embeddings from BERT with an Application to Corpus Exploration~// Proceedings of EMNLP. --- 2021.
	
	\bibitem{pmc_siamese2022}
	
	Hybrid approach of BERT extraction with deep Siamese Bi-LSTM for semantic text similarity~// Scientific Reports. --- 2022.
	
	\bibitem{arxiv_lstm_plag2021}
	
	An LSTM-based Plagiarism Detection via Attention Mechanism and a Population-Based Approach for Pre-training Parameters with Imbalanced Dataset~// arXiv preprint. --- 2021.
	
	\bibitem{acl_intrinsic_2015}
	
	Intrinsic Plagiarism Detection~// Proceedings of the ACL Workshop. --- 2015.
	
	\bibitem{arxiv_auto_ie2024}
	
	AutoIE: Automated Information Extraction from Scientific Literature~// arXiv preprint. --- 2024.
	
	\bibitem{arxiv_citecheck2025}
	
	CiteCheck: Accurate Citation Faithfulness Detection via Semantic Graph Representation Learning~// arXiv preprint. --- 2025.
	
\end{thebibliography}